---
title: "FSB Survey Data Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
#runtime: shiny
---

```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)

#package intialization
if(require(pacman)==FALSE) install.packages("pacman")
pacman::p_load(tidyverse, #for data manipulation
               plotly, #for interactive plots
               flexdashboard, #to make a dashboard
               fontawesome, #for icons
               DT, #for better tables
               scales #for displaying numbers in currency format
               )

#read in data
data = readRDS("cleaned_FSB_survey_data.RDS")
```

# General Overview {data-orientation=columns}

An overall summary of our project
  
## row {data-width=500}

### The Question We Want to Answer

We want to know more about the macro placement and salary trends of Farmer School of Business Students by year and major. We are interested in seeing whether there are any common patterns that can be spotted from 2019 to 2021 in the dataset.

We have created two pages in our dashboard, each with insights into student placement information by year and major. These can be accessed through clicking on each tab.

Through this, we would be able to derive more insights into which year and major we should place more investment in respectively. This would allow us to devise a more effective management method for the growth and advancement of the Farmer School.

### Our Findings

From 2019 to 2021, students' GPA Ranges have slightly increased, with a lower shift from those with the "3.00 - 3.49" range and an increase in the "3.500 - 4.00" range. This is an indication of improved academic performance from our students.

In terms of salary trends, we observed variations over the years. Salaries for FSB graduates have remained relatively stable, with minor fluctuations. The year 2020 saw a peak in average salaries, while 2021 witnessed a slight decrease. Overall, FSB graduates continue to enjoy competitive salaries.

Examining placement and salary trends on a major-specific level provides insights into the performance of various academic programs. Major-specific trends indicate that certain majors consistently outperform others in terms of both placement and salary, such as Business Analytics, Information Systems, and Finance. 


## row {data-height=700}

### Overall Data Table

```{r,echo=FALSE}
datatable = data %>%
  group_by(major1, year.x) %>%
  summarize(
    student_count = n(),
    avg_salary = dollar(mean(survey_salary, na.rm = TRUE))
  ) %>%
  arrange(major1)

datatable(datatable, rownames = F, extensions = 'Buttons',
          options = list(dom = 'Bfrtip',
                         buttons = c('copy','csv','excel')
                         ))
```
# Placement by Year {data-orientation=columns}

## Column {data-width=500}

### GPA Ranges by Year

```{r,echo=FALSE}
data1 = data %>%
  group_by(GPA.Range, year.x) %>%
  summarize(count = n()) 

a = ggplot()+
  geom_col(aes(x = year.x, y = count, fill = GPA.Range),  data = data1)+
  xlab("Year")+
  ylab("Number of Responses")+
  theme_bw()+
  theme(axis.title.x = element_text(margin=margin(r=12)),
        axis.title.y = element_text(margin=margin(r=12)))

ggplotly(a)
```

### Average Salary Placement by Year

```{r,echo=FALSE}
data2 = data %>%
  drop_na(survey_salary) %>%
  group_by(year.x) %>%
  summarize(avg = mean(survey_salary))

m = ggplot()+
  geom_col(aes(x = year.x, y = avg), fill = "dodgerblue3", data = data2)+
  xlab("Year")+
  ylab("Average Salary")+
  theme_bw()+
  theme(axis.title.x = element_text(margin=margin(r=12)),
        axis.title.y = element_text(margin=margin(r=12)))

ggplotly(m)
```

## Column {data-width=600}

### Top 10 US Locations by Salary

```{r,echo=FALSE}
data3 = data %>%
  drop_na(survey_salary) %>%
  group_by(survey_state) %>%
  summarize(avg = mean(survey_salary)) %>%
  arrange(desc(avg)) %>%
  head(10)

n = ggplot()+
  geom_col(aes(x = reorder(survey_state, -avg), y = avg), 
           fill = "dodgerblue3", data = data3)+
  theme_bw()+
  theme(axis.title.y = element_text(margin=margin(r=100)))+
  xlab("State")+
  ylab("Average Salary")+
  coord_flip()

ggplotly(n)
```
# Placement by Major {data-orientation=columns}

## Column {data-width=400}

### Number of Students Having a Job at Fortune 1000 Companies By Each Major

```{r,echo=FALSE}
major_fortune = readRDS("major_fortune.RDS")
major_fortune_count <- major_fortune %>%
  group_by(major) %>%
  summarize(Count = sum(fortune == "Yes")) %>%
  filter(Count > 0) %>%
  arrange(desc(Count))

# Create a bar chart
p1 = ggplot(major_fortune_count, aes(y = reorder(major, Count), x = Count)) +
  geom_bar(stat = "identity", fill = "dodgerblue3") +
  labs(x = "Number of Students", y="") +
  theme_minimal()

ggplotly(p1)
```

### Number of Students Having Internships and Job Offers by Major

```{r,echo=FALSE}
major_offer = readRDS("major_offer.RDS")
major_offer_count <- major_offer %>%
  group_by(major) %>%
  summarize(Count_intern = sum(internships > 0),
            Count_offer = sum(offers > 0))
count_long <- pivot_longer(major_offer_count, cols = starts_with("Count"), names_to = "Count_type", values_to = "Count")

# Create a double bar chart
p2 = ggplot(count_long, aes(y = reorder(major, Count), x = Count, fill = Count_type)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(y = "") +
  scale_fill_discrete("Number of Offers", labels=c("Internship", "Job")) +
  theme_minimal()

ggplotly(p2)
```


## Column {data-width=600}

### Average Salary by Majors

```{r,echo=FALSE}
major_salary = readRDS("major_salary.RDS")

p3 = major_salary %>%
  group_by(major) %>%
  summarize(avg_salary = mean(salary)) %>%
  ggplot(aes(x = avg_salary, y = reorder(major, avg_salary))) +
  geom_bar(stat = "identity", fill = "dodgerblue3") +
  labs(x = "Average Salary ($)",
       y = "Major",
       caption = "Data Source: FSB Survey Data") +
  theme_minimal()

ggplotly(p3)
```

