---
title: "FSB Survey Data Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
#runtime: shiny
---

```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)

#package intialization
if(require(pacman)==FALSE) install.packages("pacman")
pacman::p_load(tidyverse, #for data manipulation
               plotly, #for interactive plots
               flexdashboard, #to make a dashboard
               fontawesome, #for icons
               DT #for better tables
               )

#read in data
data = readRDS("cleaned_FSB_survey_data.RDS")
```

# General Overview {data-orientation=columns}

An overall summary of our project
  
## row {data-width=600}

### The Question We Want to Answer

```{r, echo = FALSE}

```

## row {data-height=600}

### Additional Insights

```{r,echo=FALSE}

```

# Page 2 {data-orientation=columns}

## Column {data-width=400}

### Chart Name

```{r,echo=FALSE}

```

### Chart Name

```{r,echo=FALSE}

```


## Column {data-width=600}

### Chart Name

```{r,echo=FALSE}

```


# Page 3 {data-orientation=columns}

## Column {data-width=500}

### Chart Name

```{r,echo=FALSE}

```

## Column {data-width=500}

### Add Another Chart Here

```{r}

```

