---
title: "Cleaning the Combined BI And Survey Career Data"
author: "Your Name Here"
output:
  html_document:
    date: "`r format(Sys.time(), '%d %B, %Y')`"
    code_folding: hide
    df_print: paged
    number_sections: yes
    theme: cerulean
    toc: yes
    toc_float: yes
    code_download: true
  word_document:
    toc: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)

#package intialization
rm(list = ls()) # clear global environment
graphics.off() # close all graphics
if(require(pacman)==FALSE) install.packages("pacman")
pacman::p_load(DataExplorer,tidyverse,readxl,zoo,stargazer,kableExtra,skimr,plotly,ggpubr,vtable,tm)
```

# Introduction and Purpose

This project will utilize FSB Placement Data to provide information on the macro placement and salary trends over the past three years, specifically whether our results are increasing, decreasing, or being steady for FSB as a whole and by major.

# Data Sources

We will be using the FSB Survey Results from 2019 to 2021 as provided for our data analysis

## Read in the data

```{r}
data=readRDS(file = "FSB_BI_Survey_2019_2021.rds")
```

# Data Preprocessing

Describing each data preprocessing step with small chunks of code, output where necessary, and documentation

# The rest of your document

Add sections and subsections as necessary to guide your analysis

